Modelling RNA-based oscillatory circuits

### 2015-09-16 MScWriteup.tex
final changes

\begin{abstract}
For the synthetic biologist looking to engineer regulation of genetic circuitry, RNA is an attractive tool due to the ease of predicting its behaviour from physiochemical models. In this report, we introduce a system of ODEs to model a recently designed synthetic regulatory circuit, before attempting to estimate its unknown parameters using recent single cell time series data. We provide estimates for a subset of parameters, but find many of them to be inestimable. We suggest this is a consequence of translation being a rate limiting step in our ODE model and suggest that a simplified model, describing translation alone, may describe the data equally well.
\end{abstract}

@@

\cite{Rodrigo2012} proposed a computational methodology to design general genetic circuits based on RNA interactions, and as a case study of the methodology chose to design a synthetic sRNA- mRNA pair capable of acting in the manner described above. The algorithm assumed an interaction scheme between the RNA's as shown in Fig. \ref{reactionscheme}. The sRNA and mRNA, originally in their own individually folded states, would initially interact via a small 
`toehold' sequence of unpaired nucleotides to form an unstable transition state. This intermediate complex would then rapidly form a final, stable complex with the desired conformation. By finding sRNA and mRNA sequences which optimised the energy landscape shown in Fig. \ref{reactionscheme}, \cite{Rodrigo2012} suggested several sRNA-mRNA pairs which would work in tandem to form a stable hybrid with the RBS free.

@@

The data we will consider consists of two sets of individual cell time series, labelled \textit{13\_9} and \textit{14\_7} \cite{Jaramilloa}. They correspond to different experimental runs of the above apparatus, for which IPTG concentration was held constant, at a value assumed large enough to saturate the cell's response (i.e the IPTG input to the AND gate is always $1$), and aTc concentrations were varied periodically. Appendix \ref{Initial  Experimental Data} shows the full datasets, with their forcing functions. Note that \textit{13\_9} contains two different forcing periods.

@@

In \eqref{eq:s} - \eqref{eq:z}, we present a modified version an existing model which describes the system \cite{Jaramilloa}, consisting of a set of ODE's with mass action kinetics.  Its state is given by the vector $(s,m,s:m,c,p,g,z)$, with all other variables representing model parameters. Tables \ref{StateVariables} and \ref{ModelParameters} give complete descriptions of the parameters and state variables.

@@

\begin{figure*}
    \begin{subfigure}[c]{0.49\textwidth}
    \centering
    \includegraphics[scale = 0.24,clip = true, trim = 115 0 60 0]{13_9_bestPlot}
        \caption{Model prediction, using the parameter set with the smallest error value of the initial 200 found, for the \textit{13\_9} dataset.}
                \label{InitialResults_13_9_best}
    \end{subfigure}
    \begin{subfigure}[c]{0.49\textwidth}
    \centering
        \includegraphics[scale = 0.24,clip = true, trim = 100 0 70 0]{14_7_bestPlot}
        \caption{Model prediction, using the parameter set with the smallest error value of the initial 200 found, for the \textit{14\_7} dataset.}
        \label{InitialResults_14_7_best}
    \end{subfigure}
        \begin{subfigure}[h]{0.49\textwidth}
    \centering
        \includegraphics[scale = 0.24, clip = true, trim = 130 0 125 0]{13_9_hist}
        \caption{Histogram of estimated parameter values, found from 200 runs of the CMA-ES algorithm. Fitted to the \textit{13\_9} dataset.}
        \label{InitialResults_13_9_hist}
    \end{subfigure}
    \begin{subfigure}[c]{0.49\textwidth}
    \centering
        \includegraphics[scale = 0.24,clip = true, trim = 130 0 125 0]{14_7_hist}
        \caption{Histogram of estimated parameter values, found from 200 runs of the CMA-ES algorithm. Fitted to the \textit{14\_7} dataset. }
        \label{InitialResults_14_7_hist}
    \end{subfigure}
    \caption{Parameter estimates and model predictions for the \textit{13\_9} and \textit{14\_7} datasets. Note that in the model predictions, aTc forcing is shown - IPTG concentration is constant at a level which saturates the cell's response. The forcing curve's height is schematic - aTc concentration is switched between off and on (where by `on' we mean a level which saturates the cell's response).}
\label{InitialResults}
\end{figure*}

@@

 \begin{figure}[h!]	
 	\begin{subfigure}[h]{0.49\textwidth}
    \centering
        \includegraphics[scale = 0.3,clip = true, trim = 70 0 70 0]{13_9_partial_data_13_9_pred}
        \caption{Model trained on \textit{13\_9}  60/60 data only, full prediction}
        \label{CrossValidation_1} 
    \end{subfigure}
	\begin{subfigure}[h]{0.49\textwidth}
    \centering
        \includegraphics[scale = 0.3,clip = true, trim = 70 0 70 0]{14_7_pred_13_9_data}
        \caption{\textit{14\_7} prediction \textit{13\_9} data}
        \label{CrossValidation_2} 
    \end{subfigure}
    \begin{subfigure}[h]{0.49\textwidth}
    \centering
        \includegraphics[scale = 0.3,clip = true, trim = 70 0 70 0]{13_9_pred_14_7_data}
        \caption{\textit{13\_9} prediction \textit{14\_7} data}
        \label{CrossValidation_3} 
    \end{subfigure}
    \caption{Cross validating data by taking parameter estimates from one dataset, and using them to predict another. \ref{CrossValidation_1} shows model predictions for the full \textit{13\_9} dataset, when only trained on the first forcing period data. \ref{CrossValidation_2}, \ref{CrossValidation_3} show model predictions for fitting to one dataset, and predicting the other.}
\label{CrossValidation}   
\end{figure}

@@

\begin{figure}[h]	
	\begin{subfigure}[h]{0.49\textwidth}
    \centering
        \includegraphics[scale = 0.23,clip = true, trim = 110 0 60 0]{Sensitivity_unscaled}
        \caption{Unscaled}
        \label{SensitivityMatrix_unscaled} 
    \end{subfigure}
    \begin{subfigure}[h]{0.49\textwidth}
    \centering
        \includegraphics[scale = 0.23,clip = true, trim = 70 0 60 0]{Sensitivity_scaled}
        \caption{Scaled}
                \label{SensitivityMatrix_scaled} 
    \end{subfigure}
    \caption{Sensitivity coefficients $S_{ij}$ \eqref{eq:Sensitivity}, evaluated about a set of estimated parameters from the \textit{13\_9} dataset, for a single oscillation. \ref{SensitivityMatrix_unscaled} shows them unscaled, \ref{SensitivityMatrix_scaled} shows them scaled by the norm of each column of $S$.} 
\label{SensitivityMatrix}   
\end{figure}

We see that many of the parameters give sensitivity curves of similar shapes, and have near linear dependence - this implies that the effects of perturbing any one of these parameters all look similar in terms of model output, and are hard to distinguish between. This may help to explain why some of our initial parameter estimates are very loose - this result suggests there is a family of parameters all of which, in terms of the model output we have available, cannot be resolved. As such, we should view estimates of these parameters with extreme caution. Note that the sensitivity curve that looks least similar to the others in Fig. \ref{SensitivityMatrix_scaled} - $\mu$ - corresponds to a relatively tightly estimated value in Fig. \ref{InitialResults}. Note also that the curve for $\Theta$ is very similar to those for the remaining parameters. This suggests that our estimated value of $\Theta$ in Fig. \ref{InitialResults_13_9_hist} is misleading, and likely a consequence of the initial bounding box.

@@

 We note that \ref{13_9_scatterplot_simplified} shows a strong positive correlation between the minima found for $F$ and $\Theta$. This is consistent with the  normalised sensitivity curves for the \textit{13\_9} dataset, shown in Fig. \ref{Sensitivity_scaled_simplified}. As before, the similarity of the $F$ and $\Theta$ curves suggests that any minima in $F - \Theta$ space will be locally non-unique \cite{Beck}.

@@

 We also note that the parameter estimates come in two distinct clusters.  We further investigate by fixing the value of $\Theta$, and plotting the error as a function of $\mu$ and $F$. Results are shown in Fig. \ref{SimplifiedModelLikelihood}. We find a basin in $ \mu - F$ space, pocketed by many local minima of similar fitness values. The optimisation algorithm will always terminate in one of these local minima, explaining the disconnected clusters shown in Fig.  \ref{13_9_scatterplot_simplified}. Thus the tightness of each peak in Fig. \ref{13_9_hist_simplified} is misleading - the uncertainty in parameter estimates is better reflected by the contours of Fig. \ref{Likelihood_profile_fine}.

@@

In this report, we have presented a system of ODE's to model a recently proposed synthetic RNA regulatory circuit \cite{Rodrigo2012}, and attempted to estimate the model's parameters using existing time series data, with a least squares minimisation approach similar to that found in recent synthetic biology literature \cite{Hu2015}. We have found many of the parameters contained in the full model to be inestimable, and suggested reasons for this. We have further suggested a simplified model, which provides an equally good description of the data with fewer parameters than the initial model.

@@

Another approach might be to use Markov Chain Monte Carlo (MCMC) to perform a Bayesian parameter estimation \cite{Jitjareonchai2006,Andrieu2003}. This method would explicitly provide us with marginal distributions of parameter probabilities, giving a more complete picture of the best parameter sets and their uncertainties than we currently have - we would still be able to pick out a maximum likelihood point estimator, as we do now, but rather than getting an ad hoc picture of the uncertainty in the parameters by repeatedly running the minimisation algorithm, the marginals would give us this information directly. However, this change in methodology would not have allowed us to gain estimates of the parameters in the original model, and is not necessary for the simplified one. It may be useful to use in place of the least squares approach if further modelling of the translation step is pursued.

@@

\section{Additional Initial Results figures}
\label{Additional Initial Results figures}
\setcounter{figure}{0}

\begin{figure}[H]
    \begin{subfigure}[c]{0.49\textwidth}
        \centering
    \includegraphics[scale = 0.235, clip = true, trim = 120 0 65 0]{13_9_heatmap.eps}
        \caption{Correlation matrix of estimated parameter sets, from the  \textit{13\_9} dataset. }
        \label{InitialResults_13_9_correlation}
    \end{subfigure}
    \begin{subfigure}[c]{0.49\textwidth}
    \centering
        \includegraphics[scale = 0.235, clip = true, trim = 80 0 70 0]{14_7_heatmap.eps}
        \caption{Correlation matrix of estimated parameter sets, from the  \textit{14\_7} dataset.}
        \label{InitialResults_14_7_correlation}
    \end{subfigure}

       \begin{subfigure}[c]{0.49\textwidth}
        \centering
    \includegraphics[scale = 0.35, clip = true, trim = 0 0 0 0]{13_9_f_hist}
        \caption{Error values found from 200 initial parameter estimates, \textit{13\_9 dataset}. }
        \label{InitialResults_13_9_f}
    \end{subfigure}
    \begin{subfigure}[c]{0.49\textwidth}
    \centering
        \includegraphics[scale = 0.35, clip = true, trim = 0 0 0 0]{14_7_f_hist}
        \caption{Error values found from 200 initial parameter estimates, \textit{14\_7 dataset}}
        \label{InitialResults_14_7_f}
    \end{subfigure}
    \caption{Inter-parameter correlation values and error function values, found from 200 initial parameter estimates, for the \textit{13\_9} and \textit{14\_7} datasets.}     
\label{InitialResults_additional}
\end{figure}

@@

\begin{figure}[h]	
    \centering
        \includegraphics[scale = 0.25]{13_9_f_simplified}
        \caption{}
        \label{13_9_f_simplified} 
\end{figure}

@@

We note that it is possible that this separation of timescales is an artefact of the fitting, and not necessarily true of the system. We can only evaluate model predictions on the parameter sets the algorithm returns us, and it seems the case that the parameter sets found by the algorithm have this feature. Hypothetically, there may exist parameter sets where all state variables vary on a similar timescale - all we can say is that, in the search region specified, the algorithm has not found any which give a low error.

We also note that while some parameters may be hard to get any realistic bounds on, values for others - $\mu, \Theta$ for example - may already be available.

This point raises another issue - the arbitrary nature of the initial bounding box. Without good biological constraints on most parameter values, they have been bounded loosely and not necessarily sensibly. Rate constants can vary by many orders of magnitude, and it may be possible that the true optimum lies entirely outside the bounding box specified. Equally,  when our fitness function has turned out to be very flat in some directions, or multimodal, good biologically motivated parameter bounds may be needed to ensure our minimisation algorithm does not wander outside realistic parameter space - the algorithm may present several equally good regions of parameter space, and improved bounds will help us choose between them.

 The model may also have general structural issues. \cite{Mclean2012, Grewal1976} give general tests which can be applied to a system of ODEs to determine if all parameters are in principle estimable, and apply them successfully to models with comparable numbers of parameters to ours.

 Thus, further work may consist of tightening the bounds on parameter values, carrying out a structural analysis, and possibly simplifying the model. A much simpler phenomenological model, consisting of  just \eqref{eq:p} and \eqref{eq:g}, may explain existing data perfectly well without the need for inestimable parameters. Experimentally, one option  may be to use different forcing functions. The effect of this on parameter estimability might be anticipated by running a sensitivity analysis using this new forcing, to see if the form of Fig. \ref{SensitivityMatrix} (which shows model predictions for all states) changes. Another option, though perhaps experimentally infeasible, would be to directly observe other components of the state vector - $s$, $m$, $s:m$ and $c$. This would improve parameter estimates by giving direct observations of the effects of parameters contained in \eqref{eq:s} - \eqref{eq:c}.

 , and that the values of $\mu$ and $\Theta$ shown in Fig. \ref{13_9_hist_simplified} differ from those found in the initial fitting, Fig. \ref{InitialResults_13_9_hist} - in particular, $\Theta$ has increased beyond the upper bound initially specified. The clustering of values suggests that there may be several disconnected local minima, all with similar error values. Within each of these minima, $\Theta$ and $\mu$ will show tight clustering.

  The initial upper bound on $\Theta$ set in table \ref{Parameter_literature_review_table} will cut off some of these minima

  This may be explained with reference to the clustering of parameter estimatees \ref{13_9_scatterplot_simplified}, which shows that

Finally, we note that that \ref{13_9_scatterplot_simplified}

  shows two distinct clusters of parameter sets,

Figs. \ref{InitialResults_13_9_correlation}, \ref{InitialResults_14_7_correlation} show correlation matrices between parameter sets\footnote{These are computed by viewing each of the estimated parameter sets as a sample from a multivariate random variable. An element of the correlation matrix $R_{ij}$ is then the Pearson correlation coefficient between the $i^\mathrm{th}$ and $j^\mathrm{th}$ random variable - or, in our case, the $i^\mathrm{th}$ and $j^\mathrm{th}$ parameters}. These correlation matrices indicate that there are spaces of parameters within which the fitness function remains approximately constant - for example, in both datasets there exists a positive correlation between values of $\mu$ and $\beta$. Referring to \eqref{eq:p}, this makes heuristic sense - the two parameters may have similar effects on model predictions, and may be able to co-vary in such a way as to leave the model prediction unchanged.

>>>>

\begin{abstract}
For the synthetic biologist looking to engineer regulation of genetic circuitry, RNA is an attractive tool due to the ease of predicting its behaviour from physiochemical models. In this report, we introduce a system of ODEs to model a recently designed synthetic regulatory circuit, before attempting to estimate its unknown parameters using recent single cell time series data. We provide estimates for a subset of parameters, but find many of them to be inestimable. We suggest this is a consequence of translation being a rate limiting step in our ODE model and propose a simplified model, describing translation alone, which we show to fit data as well as the original model.
\end{abstract}

@@

\cite{Rodrigo2012} proposed a computational methodology to design general genetic circuits based on RNA interactions, and as a case study chose to design a synthetic sRNA- mRNA pair capable of acting in the manner described above. The algorithm assumed an interaction scheme between the RNA's as shown in Fig. \ref{reactionscheme}. The sRNA and mRNA, originally in their own individually folded states, would initially interact via a small 
`toehold' sequence of unpaired nucleotides to form an unstable transition state. This intermediate complex would then form a final, stable complex with the desired conformation. By finding sRNA and mRNA sequences which optimised the energy landscape shown in Fig. \ref{reactionscheme}, \cite{Rodrigo2012} suggested several sRNA-mRNA pairs which would work in tandem to form a stable hybrid with the RBS free.

@@

The data we will consider consists of two sets of individual cell time series, labelled \textit{13\_9} and \textit{14\_7} \cite{Jaramilloa}. They correspond to different experimental runs of the above apparatus, for which IPTG concentration was held constant, at a value assumed large enough to saturate the cell's response (i.e the IPTG input to the AND gate is always a logical $1$), and aTc concentrations were varied periodically. Appendix \ref{Initial  Experimental Data} shows the full datasets, with their forcing functions. Note that \textit{13\_9} contains two different forcing periods.

@@

In \eqref{eq:s} - \eqref{eq:z}, we present a modified version an existing model which describes the system discussed above \cite{Jaramilloa}, consisting of a set of ODE's with mass action kinetics.  Its state is given by the vector $(s,m,s:m,c,p,g,z)$, with all other variables representing model parameters. Tables \ref{StateVariables} and \ref{ModelParameters} give complete descriptions of the parameters and state variables.

@@

\begin{figure*}
    \begin{subfigure}[c]{0.49\textwidth}
    \centering
    \includegraphics[scale = 0.24,clip = true, trim = 115 0 60 0]{13_9_bestPlot}
        \caption{Model prediction, using the parameter set with the smallest error value of the initial 200 found, for the \textit{13\_9} dataset.}
                \label{InitialResults_13_9_best}
    \end{subfigure}
    \begin{subfigure}[c]{0.49\textwidth}
    \centering
        \includegraphics[scale = 0.24,clip = true, trim = 100 0 70 0]{14_7_bestPlot}
        \caption{Model prediction, using the parameter set with the smallest error value of the initial 200 found, for the \textit{14\_7} dataset.}
        \label{InitialResults_14_7_best}
    \end{subfigure}
        \begin{subfigure}[h]{0.49\textwidth}
    \centering
        \includegraphics[scale = 0.24, clip = true, trim = 130 0 125 0]{13_9_hist}
        \caption{Histogram of estimated parameter values, found from 200 runs of the CMA-ES algorithm. Fitted to the \textit{13\_9} dataset.}
        \label{InitialResults_13_9_hist}
    \end{subfigure}
    \begin{subfigure}[c]{0.49\textwidth}
    \centering
        \includegraphics[scale = 0.24,clip = true, trim = 130 0 125 0]{14_7_hist}
        \caption{Histogram of estimated parameter values, found from 200 runs of the CMA-ES algorithm. Fitted to the \textit{14\_7} dataset. }
        \label{InitialResults_14_7_hist}
    \end{subfigure}
    \caption{Parameter estimates and model predictions for the \textit{13\_9} and \textit{14\_7} datasets. Note that in the model predictions, aTc forcing is shown - IPTG concentration is constant at a level which saturates the cell's response. The forcing curve's height is schematic - aTc concentration is switched between off and on (where by `on' we mean a level which saturates the cell's response).}
\label{InitialResults}
\vspace{-5mm}
\end{figure*}

@@

 \begin{figure}[h!]	
 	\begin{subfigure}[h]{0.49\textwidth}
    \centering
        \includegraphics[scale = 0.3,clip = true, trim = 70 0 70 0]{13_9_partial_data_13_9_pred}
        \caption{Model trained on \textit{13\_9}  60/60 data only, full prediction}
        \label{CrossValidation_1} 
    \end{subfigure}
	\begin{subfigure}[h]{0.49\textwidth}
    \centering
        \includegraphics[scale = 0.3,clip = true, trim = 70 0 70 0]{14_7_pred_13_9_data}
        \caption{\textit{14\_7} prediction \textit{13\_9} data}
        \label{CrossValidation_2} 
    \end{subfigure}
    \begin{subfigure}[h]{0.49\textwidth}
    \centering
        \includegraphics[scale = 0.3,clip = true, trim = 70 0 70 0]{13_9_pred_14_7_data}
        \caption{\textit{13\_9} prediction \textit{14\_7} data}
        \label{CrossValidation_3} 
    \end{subfigure}
    \caption{Cross validating data by taking parameter estimates from one dataset, and using them to predict another. \ref{CrossValidation_1} shows model predictions for the full \textit{13\_9} dataset, when only trained on the first forcing period data. \ref{CrossValidation_2}, \ref{CrossValidation_3} show model predictions for fitting to one dataset, and predicting the other.}
\label{CrossValidation}
\vspace{-5mm}   
\end{figure}

@@

\begin{figure}[t]	
	\begin{subfigure}[h]{0.49\textwidth}
    \centering
        \includegraphics[scale = 0.23,clip = true, trim = 110 0 60 0]{Sensitivity_unscaled}
        \caption{Unscaled}
        \label{SensitivityMatrix_unscaled} 
    \end{subfigure}
    \begin{subfigure}[h]{0.49\textwidth}
    \centering
        \includegraphics[scale = 0.23,clip = true, trim = 70 0 60 0]{Sensitivity_scaled}
        \caption{Scaled}
                \label{SensitivityMatrix_scaled} 
    \end{subfigure}
    \caption{Sensitivity coefficients $S_{ij}$ \eqref{eq:Sensitivity}, evaluated about a set of estimated parameters from the \textit{13\_9} dataset, for a single oscillation. \ref{SensitivityMatrix_unscaled} shows them unscaled, \ref{SensitivityMatrix_scaled} shows them scaled by the norm of each column of $S$.} 
\label{SensitivityMatrix}   
\end{figure}

We see that many of the parameters give sensitivity curves of similar shapes, and have near linear dependence - this implies that the effects of perturbing any one of these parameters all look similar in terms of model output, and are hard to distinguish between \footnote{We show only a single parameter set, but the curves are a similar shape across all estimated sets - in fact, in the majority the similarity is more striking - see Fig. \ref{Sensitivity_scaled_other} for a typical set of curves.}. This may help to explain why some of our initial parameter estimates are very loose - this result suggests there is a family of parameters all of which, in terms of the model output we have available, cannot be resolved. As such, we should view estimates of these parameters with extreme caution. Note that the sensitivity curve that looks least similar to the others in Fig. \ref{SensitivityMatrix_scaled} - $\mu$ - corresponds to a relatively tightly estimated value in Fig. \ref{InitialResults}. Note also that the curve for $\Theta$ is very similar to those for the remaining parameters. This suggests that our estimated value of $\Theta$ in Fig. \ref{InitialResults_13_9_hist} is misleading, and likely a consequence of the initial bounding box.

@@

 We note that \ref{13_9_scatterplot_simplified} shows a strong positive correlation between the minima found for $F$ and $\Theta$. This is consistent with the  normalised sensitivity curves, shown in Fig. \ref{Sensitivity_scaled_simplified}\footnote{We display the curves evaluated using the parameter set giving the lowest error, but they are similar in all estimated parameter sets.}. As before, the similarity of the $F$ and $\Theta$ curves suggests that any minima in $F - \Theta$ space will be locally non-unique \cite{Beck} - where these parameters do have distinguishable effects on model prediction is in the tail of fluorescence decay. We also note that the parameter estimates come in two distinct clusters - we expect this is due to  the error landscape containing many local minima of similar error value.

 We may further investigate the error landscape by fixing the value of $\Theta$, and varying $\mu$ and $F$. Results are shown in Fig. \ref{SimplifiedModelLikelihood}, for $\Theta = 5400$ (the modal value of $\Theta$ in Fig. \ref{13_9_hist_simplified}). We find a basin in $ \mu - F$ space, pocketed by many local minima clustered around one of the peaks in Fig. \ref{13_9_hist_simplified}. Note that the tightness of the peak in Fig. \ref{13_9_hist_simplified}  does a poor job of representing the uncertainty in $\mu$ for a given $\Theta$ - the countours of Fig. \ref{Likelihood_profile_rough} are a better measure.

 We also note consistency between minima found by the simplified model and the more complex one. Setting $\Theta = 1000$ (Fig. \ref{Likelihood_profile_theta_1000}), we find minima at $\mu \approx 0.045$, $F \approx 235$, the $\mu$ and $\beta m +f_{s}\beta c$ values shown in Figs. \ref{InitialResults_13_9_hist} and \ref{fixedpoint_f}.

@@

@@

In this report, we have presented a system of ODEs to model a recently proposed synthetic RNA regulatory circuit \cite{Rodrigo2012}, and attempted to estimate the model's parameters using existing time series data, with a least squares minimisation approach similar to that found in recent synthetic biology literature \cite{Hu2015}. We have found many of the parameters contained in the full model to be inestimable, and suggested reasons for this. We have further suggested a simplified model, which provides an equally good description of the data with fewer parameters than the initial model.

@@

Another approach might be to use Markov Chain Monte Carlo (MCMC) to perform a Bayesian parameter estimation \cite{Jitjareonchai2006,Andrieu2003}. This method would explicitly provide us with marginal distributions of parameter probabilities, giving a more complete picture of the best parameter sets and their uncertainties than we currently have - we would still be able to pick out a maximum likelihood point estimator, as we do now, but rather than getting an ad hoc picture of the uncertainty in the parameters by repeatedly running the minimisation algorithm, the marginals would give us this information directly. Having said this, a change in methodology would not have allowed us to gain estimates of the parameters in the original model - it may be worth using in place of the least squares approach if further modelling of the translation step is pursued.

@@

\section{Initial fitting additional results}
\label{Additional Initial Results figures}
\setcounter{figure}{0}

\begin{figure}[H]

       \begin{subfigure}[c]{0.49\textwidth}
        \centering
    \includegraphics[scale = 0.35, clip = true, trim = 0 0 0 0]{13_9_f_hist}
        \caption{Error values found from 200 initial parameter estimates, \textit{13\_9 dataset}. }
        \label{InitialResults_13_9_f}
    \end{subfigure}
    \begin{subfigure}[c]{0.49\textwidth}
    \centering
        \includegraphics[scale = 0.35, clip = true, trim = 0 0 0 0]{14_7_f_hist}
        \caption{Error values found from 200 initial parameter estimates, \textit{14\_7 dataset}}
        \label{InitialResults_14_7_f}
    \end{subfigure}
    \caption{Error function values, found from 200 initial parameter estimates, for the \textit{13\_9} and \textit{14\_7} datasets.}     
\label{InitialResults_additional}
\end{figure}

\begin{figure}[h]
    \centering
        \includegraphics[scale = 0.35, clip = true, trim = 0 0 0 0]{Sensitivty_scaled_other}
        \caption{A typical set of normalised sensitivity curves found from the initial 200 sets of estimated parameters, \textit{13\_9} dataset. Note that the all curves except those for $\Theta$ and $\mu$ lie very close to one another.}
        \label{Sensitivity_scaled_other}
    \end{figure}

@@

\begin{figure}[h]	
    \centering
        \includegraphics[scale = 0.25]{13_9_f_simplified}
        \caption{Error function values, found from 400 parameter estimates using the simplified model \eqref{eq:p_simplified} - \eqref{eq:z_simplified}, for the \textit{13\_9} dataset.}
        \label{13_9_f_simplified} 
\end{figure}

\begin{figure}[h]	
    \centering
        \includegraphics[scale = 0.25]{Likelihood_profile_theta_1000}
        \caption{A basin of low error values in $\mu - F$ space, $\Theta = 1000$. Note the colour scaling maps all values above $10$ to the maximum colour.}
        \label{Likelihood_profile_theta_1000} 
\end{figure}

@@
